\documentclass[a4paper,12pt,oneside]{amsbook}

\linespread{1.05}

\usepackage{amssymb}

\usepackage{amsfonts}

% Deutsche Sprache verwenden
\usepackage{german}

% Umlaute normal eingeben
\usepackage[utf8]{inputenc}

\usepackage{graphicx}

\usepackage{tikz}

\usepackage{listings}
\renewcommand{\lstlistingname}{Code}

\usepackage{color}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}
\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}

% oben Ueberschriften
\pagestyle{headings}

\textwidth=15 cm
\textheight=22 cm
\topmargin=1.2 cm
\oddsidemargin=0.5 cm
\evensidemargin=0.5 cm
\footskip=40 pt
\parskip5pt


\begin{document}


\begin{titlepage}
\begin{center}
{\large Universität Osnabrück}


\vspace{9em}
{\LARGE \emph{Smoothed Particle Hydrodynamics}}

\vspace{2em}
{\large Tobias Graf\\ Dominik Grodt\\ Sascha Bachmann}

\vspace{9em}
{\large Projektdokumentation zur Veranstaltung\\ Parallele Algorithmen mit OpenCL\\ SoSe 2013}



\end{center}
\end{titlepage}

\tableofcontents

\input{0_Einleitung_Dominik}
\input{1_Programmstruktur_Dominik}
\input{2_SPH_Physik_Sascha}
\input{3_SPH_Implementation_Dominik}
\input{4_Visualisierung_MarchingCubes_Allgemein_Tobias}
\input{5_Visualisierung_MarchingCubes_Details_Sascha}
\input{6_Visualisierung_DeferredShading_Tobias}


\begin{thebibliography}{}


\bibitem{IntroSPH}
J.\ J.\ Monaghan (1988),
{\em An Introduction to SPH}. Computer Physics Communication, Vol. 48, pp. 89-96.


\bibitem{FlowSPH}
J.\ J.\ Monaghan (1994),
{\em Simulating Free Surface Flows with SPH}. Journal of Computational Physics, Vol. 110, pp. 399-406.


\bibitem{FluidSim}
M.\ Müller, D.\ Charypar, M.\ Gross (2003),
{\em Particle-Based Fluid Simulation for Interactive Applications}. Proceedings of the 2003 ACM SIGGRAPH/Eurographics symposium on Computer animation, pp. 154-159.


\bibitem{BoundarySPH}
T.\ Harada, S.\ Koshizuka and Y.\ Kawaguchi (2007),
{\em Improvement in the Boundary Conditions of Smoothed Particle Hydrodynamics}. Computer Graphics \& Geometry, Vol. 9, No. 3, pp. 2-15.


\bibitem{MC}
W.\ E.\ Lorensen, H.\ E.\ Cline (1987),
{\em Marching cubes: A high resolution 3D surface construction algorithm}. SIGGRAPH Comput. Graph., Vol. 21, No. 4, pp. 163-169.


\bibitem{MCADD}
W.\ Heiden, T.\ Goetze, J.\ Brickmann (1993). {\em Fast generation of molecular surfaces from 3D data fields with an enhanced ``marching cube'' algorithm}. Journal of Computational Chemistry, Vol. 14, Iss. 2, pp. 246-250.

\end{thebibliography}


\end{document}